---
title: "Network Learning 2"
author: "Miriam Weaverdyck"
date: "3/21/2020"
output: html_document
---

## Setup

```{r load packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
library(dplyr)
library(tidyr)
library(network)
library(rjson)
library(ggplot2)
library(plyr)
library(Rmisc)
library(igraph)

```


```{r variable setup, echo=F}

# set variables
structures <- c('natural', 'unnatural')
subs_to_exclude<-c(0, 994, 995, 996, 997, 998, 30, 33, 44, 71, 118, 202, 229, 230, 142, 42)
n_sect <- 2
cols <- c("#8c96c6","#88419d")

# directories
project_dir <- "~/CSNLGoogleDrive/network-learning2/"
analyze_dir <- paste0(project_dir,'analyze/')
ego_dir <- paste0(project_dir,'ego-network-task/')
learn_dir <- paste0(project_dir,'learning-task/data/')
draw_dir <- paste0(project_dir,"drawing-task/")
fig_dir <- paste0(analyze_dir, 'figures/')

```

### Read in data
True network structures
```{r, echo=F}
true_els <- read.csv(paste0(analyze_dir, "network_edges.csv"))
true_els[,c('node1', 'node2')] <- true_els[,c('node1', 'node2')] + 1
all_edges <- as.data.frame(t(combn(9,2)))
names(all_edges) <- c("node1","node2")
```

```{r, echo=F}
par(mfrow=c(1,2))
plot.network(as.network(true_els[true_els$Structure=='natural',c('node1','node2')], directed=F, matrix.type = "edgelist"),
             displaylabels=T,
             main="natural")
plot.network(as.network(true_els[true_els$Structure=='unnatural',c('node1','node2')], directed=F, matrix.type = "edgelist"),
             displaylabels=T,
             main="unnatural")
par(mfrow=c(1,1))
```

```{r read data}
# must run analyze/convert_combine_csvs.Rmd first
data_draw <- read.csv(paste0(draw_dir, "network_learn2_draw_data.csv"))
data_ego <- read.csv(paste0(ego_dir, "network_learn2_ego_data.csv"))
ego_els <- read.csv(paste0(ego_dir,"network_learn2_ego_edgelists.csv"))
data_demo <- read.csv(paste0(ego_dir,"network_learn2_demographics.csv"))
```



## Analyses
```{r accuracy by network type}

accuracy_draw <- ddply(data_draw, .(ID, Structure, Condition),
                       summarise, correct=mean(correct))

summ_accuracy_draw <- summarySEwithin(data = data_draw,
                                      measurevar = "correct",
                                      betweenvars = "Condition",
                                      withinvars = c("Structure"),
                                      idvar = "ID",
                                      na.rm = T)
```


```{r accuracy tests}
mylm <- lmerTest::lmer(correct ~ Structure + (1|ID),
                       data=accuracy_draw)
knitr::kable(anova(mylm))
# which network structure did participants learn better?
# - natural
mymeans <- emmeans::emmeans(mylm, "Structure")
knitr::kable(confint(mymeans))
knitr::kable(pairs(mymeans))
```


```{r, accuracy by network type plots, echo=F}

ggplot(accuracy_draw, aes(x=Structure, y=correct))+
  geom_boxplot()+
  geom_line(aes(group=interaction(ID)), position = position_dodge(.2),
            color="gray", alpha=.5) +
  geom_hline(yintercept=15/36, col="black", linetype=3)+
  geom_hline(yintercept=21/36, col="black", linetype=3)+
  theme(legend.position="none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust = 0.5)) +
  geom_point(aes(col=as.factor(ID)),
             position = position_dodge(.2),
             alpha = .75)
ggsave(paste0(fig_dir,"accuracy_boxplot.png"), width=6.5/2, height=3, units="in")

ggplot(summ_accuracy_draw, aes(x=Structure, y=correct))+
        geom_bar(stat="identity", position = "dodge",
                 aes(fill=Structure)) +
        scale_fill_manual(limits=structures, values=rev(cols)) +
        geom_hline(yintercept=15/36, col="black", linetype=3)+
        geom_hline(yintercept=21/36, col="black", linetype=3)+
        geom_line(data=accuracy_draw, aes(group=interaction(ID)),
                  position = position_dodge(.2),
                  color="gray", alpha=.5) +
        geom_point(data=accuracy_draw, aes(col=as.factor(ID)),
                   position = position_dodge(.2),
                   alpha = .75) +
        geom_errorbar(aes(ymin=correct-se, ymax=correct+se), width=.1)+
        theme(legend.position="none",
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              axis.line = element_line(colour = "black"),
              plot.title = element_text(hjust = 0.5)) +
        labs(x="Network Structure", y="% Accuracy") +
        ggtitle("Accuracy")
ggsave(paste0(fig_dir,"accuracy_barplot.png"), width=6.5/2, height=3, units="in")


# plot circle graphs
data_draw <- arrange(data_draw, node1, node2)
all_edges <- as.matrix(unique(data_draw[,c("node1","node2")]))
# create a graph including all possible edges
g_all <- graph_from_edgelist(all_edges, directed = FALSE)
# get average report rate
accuracy_draw_els <- ddply(data_draw, .(Condition, Structure, node1, node2, true_structure),
                            summarise,
                            prop_reported=mean(as.numeric(as.logical(sub_reported))),
                            accuracy=mean(as.numeric(correct)))
# save which edges are in each structure
in_network <- accuracy_draw_els[,c("node1","node2","true_structure", "Structure")]
in_network <- spread(in_network, Structure, true_structure)
# define general layout
x_extreme <- -1
v_space <- 1
vspace <- v_space
coords <- rbind(c(x_extreme,0),
                c(x_extreme+v_space,1*vspace),
                c(x_extreme+3*v_space,1.5*vspace),
                c(x_extreme+5*v_space,1*vspace),
                c(x_extreme+6*v_space,0),
                c(x_extreme+5*v_space,-1*vspace),
                c(x_extreme+3*v_space,-1.5*vspace),
                c(x_extreme+v_space,-1*vspace),
                c(x_extreme+3*v_space+.3,.3))
# define layout for A and B
g_all$margin <- c(0,0,0,0)
orders <- cbind(c(1,2,3,5,4,7,8,9,6),c(1,2,3,5,4,7,8,9,6))
colnames(orders) <- structures
# Plot all cells
mar=c(1,1,1,1)
par(mfrow=c(1,2),mar=c(1,1,1,1))
i=1
for (ab in rev(structures)){
  g_all$layout <- coords[order(orders[,ab]),]
  E(g_all)$color <- 'gray'
  E(g_all)[in_network[,ab]]$color <- cols[i]#'green'
  g_true <- subgraph.edges(g_all,eids = E(g_all)[in_network[,ab]])
  pos_edges <- accuracy_draw_els[accuracy_draw_els$Structure==ab,"prop_reported"]
  plot(g_all, edge.width=pos_edges*10, main=paste0(ab))
  i = i+1
}
dev.copy(png,paste0(fig_dir,'circle_plots.png'), width=6.5, height=3, units="in", res=300)
dev.off()
par(mfrow=c(1,1))

```




Check order effects  
```{r}
d <- ddply(data_draw, .(ID, Structure, Condition, Section),
                       summarise, correct=mean(correct))
summarySEwithin(data = d,
                measurevar = "correct",
                betweenvars = "Condition",
                withinvars = c("Structure", "Section"),
                idvar = "ID",
                na.rm = T)

accuracy_draw_sect <- summarySEwithin(data = data_draw,
                                           measurevar = "correct",
                                           betweenvars = "Condition",
                                           withinvars = c("Structure", "Section", "ID"),
                                           na.rm = T)
summ_accuracy_draw_sect <- summarySEwithin(data = data_draw,
                                      measurevar = "correct",
                                      betweenvars = "Condition",
                                      withinvars = c("Structure", "Section"),
                                      idvar = "ID",
                                      na.rm = T)

mylm <- lmerTest::lmer(correct ~ Structure*Section + (1|ID),
                       data=accuracy_draw_sect)
knitr::kable(anova(mylm))
# Did participants perform better in section 1 or section 2?
# - No difference for unnatural
# - Better in Section 2 for natural
mymeans <- emmeans::emmeans(mylm, ~Section|Structure)
knitr::kable(confint(mymeans))
knitr::kable(pairs(mymeans))
# Did participants learn the natural network better than the unnatural network in oth sections?
# - Yes
mymeans <- emmeans::emmeans(mylm, ~Structure|Section)
knitr::kable(confint(mymeans))
knitr::kable(pairs(mymeans))
```

```{r, echo=F}

ggplot(summ_accuracy_draw_sect, aes(x=Section, y=correct, fill=Structure))+
  geom_bar(stat="identity", position = "dodge") +
  scale_fill_manual(limits=structures, values=rev(cols)) +
  geom_errorbar(aes(ymin=correct-se, ymax=correct+se), width=.1,
                position = position_dodge(.9))+
  geom_hline(yintercept=15/36, col="black", linetype=3)+
  geom_hline(yintercept=21/36, col="black", linetype=3)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust = 0.5)) +
  labs(x="Section", y="% Accuracy") +
  ggtitle("Accuracy by section")
ggsave(paste0(fig_dir,"accuracy_bysection_barplot.png"), width=6.5/2, height=3, units="in")


```






###Ego Network Effects
```{r}
# combine drawing data and ego network meaures
data_egodraw <- left_join(accuracy_draw, data_ego)

knitr::kable(head(data_egodraw))
```


####Degree
Natural structure only  
Disappears when constraint added as a covariate
```{r}
data_egodraw$zdegree <- scale(data_egodraw$degree, center=T, scale = T)


mylm <- lmerTest::lmer(correct ~ Structure*degree + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="degree"))


mylm <- lmerTest::lmer(correct ~ Structure*log_degree + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="log_degree"))


mylm <- lmerTest::lmer(correct ~ Structure*zdegree + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="zdegree"))


"With constraint as a covariate:"
mylm <- lmerTest::lmer(correct ~ Structure*degree + log_constraint + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="degree"))

```

```{r, echo=F}
ggplot(data_egodraw, aes(x=degree, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point(position = position_jitter(height=.01)) +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Degree Effects on Accuracy",
       x="Degree", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)

ggsave(paste0(fig_dir,"accuracyperc_by_degree.png"),
       width=6.5, height=5, units="in")


ggplot(data_egodraw, aes(x=log_degree, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Degree Effects on Accuracy",
       x="log(Degree)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)


ggplot(data_egodraw, aes(x=zdegree, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Degree Effects on Accuracy",
       x="Degree (z-score)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)
```


####Strength
#####Non-normalized
```{r}

mylm <- lmerTest::lmer(correct ~ Structure*strength_close + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="strength_close"))


mylm <- lmerTest::lmer(correct ~ Structure*strength_freq + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="strength_freq"))

```

```{r, echo=F}
ggplot(data_egodraw, aes(x=strength_close, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Strength Effects on Accuracy",
       x="Strength\n(Closeness)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)



ggplot(data_egodraw, aes(x=strength_freq, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Strength Effects on Accuracy",
       x="Strength\n(Frequency)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)


```

#####Normalized
No effect
```{r}

mylm <- lmerTest::lmer(correct ~ Structure*strength_close_norm + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="strength_close_norm"))


mylm <- lmerTest::lmer(correct ~ Structure*strength_freq_norm + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="strength_freq_norm"))


# overall strength
data_egodraw$strength <- data_egodraw$strength_close_norm + data_egodraw$strength_freq_norm

mylm <- lmerTest::lmer(correct ~ Structure*strength + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="strength"))
```

```{r, echo=F}
ggplot(data_egodraw, aes(x=strength_close_norm, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, linetype=2,
              show.legend = T) +
  labs(title="Strength Effects on Accuracy",
       x="Strength\n(Closeness)", y="% Accuracy",
       color="Normalized Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)



ggplot(data_egodraw, aes(x=strength_freq_norm, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, linetype=2,
              show.legend = T)+
  labs(title="Normalized Strength Effects on Accuracy",
       x="Strength\n(Frequency)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)


ggplot(data_egodraw, aes(x=strength, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, linetype=2,
              show.legend = T) +
  labs(title="Normalized Strength Effects on Accuracy",
       x="Strength\n(Closeness + Frequency)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)
ggsave(paste0(fig_dir,"accuracyperc_by_strength.png"),
       width=6.5, height=5, units="in")
```


####Constraint
Natural structure only  
No effect when degree included as covariate
```{r}

mylm <- lmerTest::lmer(correct ~ Structure*log_constraint + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="log_constraint"))

"With Degree as a covariate:"
mylm <- lmerTest::lmer(correct ~ Structure*log_constraint + degree + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="log_constraint"))

```

```{r, echo=F}
ggplot(data_egodraw, aes(x=log_constraint, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, aes(linetype=Structure),
              show.legend = T)+
  scale_linetype(limits = structures,
                 labels = c("p < 0.05", "n.s."), name = "Significance") +
  labs(title="Brokerage Effects on Accuracy",
       x="Inverse Brokerage\n(Log Constraint)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)

ggsave(paste0(fig_dir,"accuracyperc_by_constraint.png"),
       width=6.5, height=5, units="in")
```


####Betweenness
No effect  
```{r}
mylm <- lmerTest::lmer(correct ~ Structure*betweenness + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="betweenness"))

```

```{r, echo=F}
ggplot(data_egodraw, aes(x=betweenness, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, linetype=2,
              show.legend = T)+
  labs(title="Brokerage Effects on Accuracy",
       x="Brokerage\n(Betweenness)", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)

ggsave(paste0(fig_dir,"accuracyperc_by_betweenness.png"),
       width=6.5, height=5, units="in")
```

####Transitivity
No effect  
```{r}
mylm <- lmerTest::lmer(correct ~ Structure*transitivity + (1|ID),
                       data=data_egodraw)
knitr::kable(anova(mylm))
knitr::kable(emmeans::emtrends(mylm, "Structure", var="transitivity"))

```

```{r, echo=F}
ggplot(data_egodraw, aes(x=transitivity, y=correct*100, color=Structure,
                         group=Structure, shape=Structure)) +
  facet_grid(~Condition) +
  geom_point() +
  stat_smooth(method = "lm", se = T, size=1, linetype=2, show.legend = T)+
  #theme(legend.position="none") +
  labs(title="Transitivity Effects on Accuracy",
       x="Transitivity", y="% Accuracy",
       color="Network\nStructure", shape="Network\nStructure")+
       scale_color_manual(values=cols)

ggsave(paste0(fig_dir,"accuracyperc_by_transitivity.png"),
       width=6.5, height=5, units="in")
```

Degree, strength, and constraint are highly correlated, and thus redundant.
As such, it is unclear which is responsible for learning accuracy.
```{r}
c <- colnames(data_ego)
knitr::kable(cor(select(data_ego, c[c!="ID"])))

cor.test(data_ego$degree, data_ego$log_constraint)

```


## Homophily
People are more accurate when images are of the same race  
```{r}

data_draw <- separate(data_draw, col=image1, into=c(NA,"x"), sep="-", remove=F)
data_draw <- separate(data_draw, col=x, into=c("race1", "sex1"), sep=1, remove=T)
data_draw <- separate(data_draw, col=image2, into=c(NA,"x"), sep="-", remove=F)
data_draw <- separate(data_draw, col=x, into=c("race2", "sex2"), sep=1, remove=T)
data_draw$race_homo <- data_draw$race1==data_draw$race2
data_draw$sex_homo <- data_draw$sex1==data_draw$sex2


accuracy_draw_homo <- ddply(data_draw, .(ID, Structure, Condition, race_homo),
                       summarise, correct=mean(correct))


mylm <- lmerTest::lmer(correct ~ Structure*race_homo + (1|ID),
                       data=accuracy_draw_homo)
knitr::kable(anova(mylm))
mymeans <- emmeans::emmeans(mylm, ~Structure*race_homo)
knitr::kable(pairs(mymeans))


mymeans <- emmeans::emmeans(mylm, ~race_homo)
knitr::kable(pairs(mymeans))
```

```{r, echo=F}

summ_accuracy_draw_homo <- summarySEwithin(data = data_draw,
                                      measurevar = "correct",
                                      betweenvars = "Condition",
                                      withinvars = c("Structure", "race_homo"),
                                      idvar = "ID",
                                      na.rm = T)

ggplot(summ_accuracy_draw_homo, aes(x=race_homo, y=correct, fill=Structure))+
  geom_bar(stat="identity", position = "dodge") +
  scale_fill_manual(limits=structures, values=rev(cols)) +
  geom_errorbar(aes(ymin=correct-se, ymax=correct+se), width=.1,
                position = position_dodge(.9))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust = 0.5)) +
  labs( y="% Accuracy") +
  ggtitle("Effects of racial homophily accuracy")
```



```{r}

accuracy_draw_homo <- ddply(data_draw, .(ID, Structure, Condition, sex_homo),
                       summarise, correct=mean(correct))


mylm <- lmerTest::lmer(correct ~ Structure*sex_homo + (1|ID),
                       data=accuracy_draw_homo)
knitr::kable(anova(mylm))
```


Racial homophily affects TP rates in unnatural network
(potential ceiling effect in natural network)  
No effect on false positive rates  
```{r}

data_draw$sub_reported <- as.numeric(as.logical(data_draw$sub_reported))
report_rates <- ddply(data_draw, 
                      .(ID, Structure, Section, true_structure, race_homo), 
                      summarise, 
                      pos_rate=sum(sub_reported)/length(correct)
                      )
report_rates[report_rates$true_structure, "rate"] <- "TruePositive"
report_rates[!report_rates$true_structure, "rate"] <- "FalsePositive"

mylm <- lmerTest::lmer(pos_rate ~ rate*Structure*race_homo + (1|ID),
                       data=report_rates)
knitr::kable(anova(mylm))


mymeans <- emmeans::emmeans(mylm, ~race_homo|rate)
knitr::kable(pairs(mymeans))

mymeans <- emmeans::emmeans(mylm, ~race_homo|rate*Structure)
knitr::kable(pairs(mymeans))

mymeans <- emmeans::emmeans(mylm, ~Structure|rate*race_homo)
knitr::kable(pairs(mymeans))

```


```{r, echo=F}

summ_report_rates <- summarySEwithin(data = report_rates,
                      measurevar = "pos_rate",
                      withinvars = c("Structure", "race_homo", "rate"),
                      idvar = "ID",
                      na.rm = T)


ggplot(summ_report_rates, aes(x=race_homo, y=pos_rate, fill=Structure))+
  facet_grid(rate~., scales="free") +
  geom_bar(stat="identity", position = "dodge") +
  scale_fill_manual(limits=structures, values=rev(cols)) +
  geom_errorbar(aes(ymin=pos_rate-se, ymax=pos_rate+se), width=.1,
                position = position_dodge(.9))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust = 0.5)) +
  labs( y="% Accuracy") +
  ggtitle("Effects of racial homophily on report rates")

ggsave(paste0(fig_dir,"race_homophily_effects.png"), width=6.5, height=5, units="in")
```

